% ====================
% EXPERIENCE A
% ====================
\subsection{{\large \href{https://www.jio.com/}{\textbf{Jio}}\hfill \normalsize Mumbai - MH}}
\subtext{ Software Development Engineer\hfill \small July 2022 --- Present}
\begin{zitemize}

\item \textbf{Developed REST APIs} for Digital Access Management system and optimised the existing code to reduce API response time by 20\%.

\item \textbf{Engineered AI tagging and asset parsing logic} to process 1TB+ assets efficiently using Elasticsearch, Kibana, Logstash, and Google Cloud Storage.

\item \textbf{Contributed to the business logic} of over 12 gratification projects, increasing user participation \& backend reliability.

\item \textbf{Integrated Redis and RabbitMQ} in 12+ backend projects, enhancing API response speed and supporting high-throughput, low-latency data processing.

\item \textbf{Implemented WebSocket based real-time communication} for multiplayer apps, supporting a high volume of concurrent users seamlessly.

\item \textbf{Built a cross-browser JavaScript extension} for JioPC, reducing bandwidth latency by 40\% and improving media streaming via native communication.

%\end{zitemize}
%\subtext{Frontend Developer (SDE-1) \hfill July 2022 --- July 2023}
%\begin{zitemize}

\item \textbf{Led frontend development for responsive B2B/B2C sites} (JioEngage, JioCoupons), driving 50K+ monthly visitors and dynamic CMS content management.

\item \textbf{Developed a multiplayer gratification platform} for JioCinema, scaling to 150K+ active users and ensuring seamless user experience.

\item \textbf{Upgraded codebase from Angular 8 to 14}, applying best practices to boost application performance, maintainability, and security.

\item \textbf{Mentored 5+ junior developers}, delivering KT sessions and implementing Agile methodologies to enhance team productivity and code quality.

\end{zitemize}


% ====================
% EXPERIENCE B
% ====================
\subsection{{\large \href{https://www.eshopbox.com/}{\textbf{Eshopbox}}\hfill \normalsize Pune - MH}}
\subtext{Software Engineer \hfill \small Jan 2022 - July 2022}
\begin{zitemize}

\item \textbf{Gained practical expertise in the MongoDB, Express, Angular \& Node.js} by building a customer portal from scratch.

\item \textbf{Boosted performance by 20\%} using modular development, efficient schema, and seamless client-server integration.

\end{zitemize}